Re-fit

### 2022-06-15 scripts/r/04_refit/refit_sc.Rmd
♻️ - edit refit sc

```{r setup}
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(plyr)
library(brms)
```

@@

@@

Script missing.

```{r}

```

@@

```{r}
paralichthys_undulatus_1_f0_cat <- brm(
  RangeST ~ Word.type + Typicality + (1|Speaker) + (1|Word),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/paralichthys_undulatus_1_f0_cat"
)
```

@@

@@

100% divergent transitions.

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(plyr)
library(mgcv)
library(brms)
```

@@

Difficult case.

@@

```{r}
msa_data <- read.csv("./data/analyses/sc/neosilurus_omanensis/annotated_cleaned_data_v7.csv", stringsAsFactors = T, header = T) %>%
  mutate(
    effect_cat = factor(typ_cat, levels = c("atypical", "medium", "typical"))
  )

contrasts(msa_data$Condition) <- "contr.sum"
```

```{r}
neosilurus_omanensis_1_f0rat_cat <- brm(
  PitchRatioAtoU ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_1_f0rat_cat"
)

neosilurus_omanensis_2_f0ranrat_cat <- brm(
  PitchRangeRatioAtoU ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_2_f0ranrat_cat"
)

# Convergence issues
neosilurus_omanensis_3_f0varrat_cat <- brm(
  PitchVariationRatioAtoU ~ effect_cat * Condition + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat"
)

neosilurus_omanensis_4_f0riserat_cat <- brm(
  PitchRiseRatio ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_4_f0riserat_cat"
)

# Convergence issues
neosilurus_omanensis_5_srrat_cat <- brm(
  SpeechRateRatioAtoU ~ effect_cat * Condition + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_5_srrat_cat"
)
```

@@

```{r}
paralichthys_undulatus_1_f0_cat <- brm(
  RangeST ~ Word.type + effect_cat + (1|Speaker) + (1|Word),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/paralichthys_undulatus_1_f0_cat"
)
```

@@

```{r}
load("./data/analyses/sc/petauroides_fistulator/mdl_data.RData")

msa_data <- mdl_data %>%
  mutate(
    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical"))
  )
```

```{r}
petauroides_fistulator_1_f0_cat <- gam(
  pitch_st ~
    effect_cat +
    s(id) +
    s(trial, bs = "re") +
    s(speaker, bs = "re") +
    s(target_name, bs = "re") +
    s(target_colour, bs = "re") +
    s(competitor_name, bs = "re") +
    s(competitor_colour, bs = "re") +
    s(distractor1_name, bs = "re") +
    s(distractor1_colour, bs = "re") +
    s(distractor2_name, bs = "re") +
    s(distractor2_colour, bs = "re"),
  data = msa_data
)

saveRDS(petauroides_fistulator_1_f0_cat, "./data/analyses/models/petauroides_fistulator_1_f0_cat.rds")
```

@@

Convergence issues.
